---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# modregplot

<!-- badges: start -->
<!-- badges: end -->

The modregplot package creates simple slopes plots from a moderated regression equation. It is useful when you are planning an analysis and want to see what your hypothesized effects would look like. You can also use it to see what simple slopes would look like from published findings that have no accompanying plots.

## Installation

You can install the released version of modregplot from [github](https://github.com) with:

``` r
remotes::install_github("wjschne/modregplot")
```

## Example

Suppose you see a moderated regression result:

$Aggression=5.5+2.1Psychopathy+0.5Impulsivity+1.2Psychopathy\cdot Impulsvity$

What will this result look like? Suppose that a high value of impulsivity is 1 and a low value is -1.

```{r example}
library(modregplot)

modregplot(
  predictor_range = c(-2, 2),
  moderator_values = c(Low = -1, High = 1),
  intercept = 5.5,
  predictor_coef = 2.1,
  moderator_coef = 0.5,
  interaction_coef = 1.2,
  predictor_label = "Psychopathy",
  criterion_label = "Aggression",
  moderator_label = "Impulsivity"
)
```

